---
title: "PCA code"
author: "Kevin Cunningham"
date: "6/29/2021"
output: html_document
editor_options: 
  chunk_output_type: inline
---

```{r}
library("FactoMineR")
library("stats")
library("factoextra")
library("ggfortify")
```


```{r}
quantile_df <- read.csv("/Users/Kevin/Desktop/Grad school docs and past classes/New_RA_Project_code/PCA/after_quantile_reduced_set.csv")
```



```{r}
quantile_table <- quantile_df[,1:1622]
print(quantile_table)
```

```{r}
pca1 <- PCA(quantile_table, scale.unit = FALSE, ncp = 5, graph= T)
```

```{r}
plot(pca1)
```




```{r}
pca2 <- prcomp(quantile_table, scale. = F)
#print(pca2)
```

```{r}
autoplot(pca2, data = quantile_df, colour = 'Sample_Status', frame.type = 'norm')
```

```{r}
pca3 <- prcomp(quantile_table, scale. = T)
#print(pca2)
```

```{r}
autoplot(pca3, data = quantile_df, colour = 'Sample_Status', frame.type = 'norm')
```




```{r}
fviz_contrib(pca2, choice = "var", axes = 1, top = 10, xtickslab.rt=90)
```

Use the top 5 features from dimension 1
1. RBPJ
2. IGHG1
3. MX1
4. TPM1
5. KRT19

```{r}
fviz_contrib(pca2, choice = "var", axes = 2, top = 10, xtickslab.rt=90)
```

Use the top 5 features from dimension 2
1. IGHG1
2. MX1
3. PKNOX1
4. KRT19
5. RBPJ





Use the top 5 features from both
1. RBPJ (x2)
2. IGHG1 (x2)
3. MX1 (x2)
4. TPM1
5. KRT19 (x2)
6. IGHG1
7. MX1
8. PKNOX1
9. KRT19
10. RBPJ

Remove duplicates
1. RBPJ
2. IGHG1
3. MX1
4. TPM1
5. KRT19
6. PKNOX1

quantile_df has all the data
Make into a dataframe
```{r}
PCA_features <- as.data.frame(matrix(data = 0, nrow = 94, ncol = 1))
PCA_features$V1 <- quantile_df$RBPJ
colnames(PCA_features) <- cbind("RBPJ")
PCA_features$IGHG1 <- quantile_df$IGHG1
PCA_features$MX1 <- quantile_df$MX1
PCA_features$TPM1 <- quantile_df$TPM1
PCA_features$KRT19 <- quantile_df$KRT19
PCA_features$PKNOX1 <- quantile_df$PKNOX1
PCA_features$Sample_Status <- quantile_df$Sample_Status
PCA_features$Case_ID <- quantile_df$Case_ID
#View(PCA_features)
```


All 6 features plus the sample status and case ID are in
the dataframe "PCA_features"


